%-------------------------
% Resume - Sukhrobbek Ilyosbekov
% PhD / Research-focused CV
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{tabularx}

% Colors
\definecolor{accent}{HTML}{2B5797}
\definecolor{darktext}{HTML}{1A1A1A}
\definecolor{lighttext}{HTML}{444444}
\definecolor{linkcolor}{HTML}{0563C1}
\definecolor{rulecolor}{HTML}{2B5797}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdfborderstyle={/S/U/W 0},
}

% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Section formatting - colored rule
\titleformat{\section}{
    \color{darktext}\large\bfseries\scshape
}{}{0em}{}[{\color{rulecolor}\vspace{2pt}\titlerule\vspace{1pt}}]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Tighter list spacing
\setlist[itemize]{leftmargin=1.4em, itemsep=1pt, parsep=0pt, topsep=2pt}
\setlist[description]{leftmargin=0pt, labelsep=0.5em, font=\bfseries\color{darktext}, style=unboxed, itemsep=1pt}

% --- Education: university + date on first line, details as bullets ---
\newcommand{\educationEntry}[2]{%
    \vspace{2pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\color{accent}#1} & \textit{\color{lighttext}#2} \\
    \end{tabular*}\vspace{-3pt}
}

% --- Experience: role | company | location, date right-aligned ---
\newcommand{\experienceEntry}[4]{%
    \vspace{5pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\color{darktext}#1} {\color{lighttext}\textbar} {\color{accent}#2} {\color{lighttext}\textbar} {\color{lighttext}#3} & \textit{\color{lighttext}#4} \\
    \end{tabular*}\vspace{-4pt}
}

% --- Experience: no location variant ---
\newcommand{\experienceEntryNoLoc}[3]{%
    \vspace{5pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\color{darktext}#1} {\color{lighttext}\textbar} {\color{accent}#2} & \textit{\color{lighttext}#3} \\
    \end{tabular*}\vspace{-4pt}
}

% --- Research project: name + link right-aligned ---
\newcommand{\projectHeading}[2]{%
    \vspace{4pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        {\textbf{\color{accent}#1}} & {\small\href{#2}{\color{linkcolor}GitHub}} \\
    \end{tabular*}\vspace{-4pt}
}

% --- Research project: with paper link ---
\newcommand{\projectHeadingPaper}[3]{%
    \vspace{4pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        {\textbf{\color{accent}#1}} & {\small\href{#2}{\color{linkcolor}GitHub} \enspace\color{lighttext}\textbar\enspace \href{#3}{\color{linkcolor}Paper}} \\
    \end{tabular*}\vspace{-4pt}
}

% --- Personal project: name + link right-aligned, description as bullet ---
\newcommand{\personalProject}[3]{%
    \vspace{4pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        {\textbf{\color{accent}#1}} & {\small\href{#3}{\color{linkcolor}#3}} \\
    \end{tabular*}\vspace{-4pt}
    \begin{itemize}
        \item #2
    \end{itemize}\vspace{-2pt}
}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\bfseries\color{darktext} Sukhrobbek Ilyosbekov}\vspace{4pt}\\
    {\large\color{accent} Computer Vision \enspace\textperiodcentered\enspace Deep Learning \enspace\textperiodcentered\enspace Explainable AI}\vspace{8pt}\\
    {\color{lighttext}
    \faPhone\enspace(857) 867-1942 \quad
    \faEnvelope\enspace\href{mailto:ilyosbekov.s@northeastern.edu}{ilyosbekov.s@northeastern.edu} \quad
    \faGlobe\enspace\href{https://suxrobgm.net}{suxrobgm.net} \quad
    \faLinkedin\enspace\href{https://www.linkedin.com/in/suxrobgm}{linkedin.com/in/suxrobgm} \quad
    \faGithub\enspace\href{https://github.com/suxrobgm}{github.com/suxrobgm}
    }
\end{center}

%----------RESEARCH INTERESTS----------
\section{Research Interests}
Computer Vision, Deep Learning, Medical Image Analysis, Explainable AI, Object Detection and Segmentation

%----------EDUCATION----------
\section{Education}

\educationEntry{Northeastern University, Boston, MA}{January 2024 -- May 2026}
\begin{itemize}
    \item Master of Science in Computer Science; GPA: 4.0/4.0
    \item Relevant Coursework: CS 7180 Advanced Perception, Machine Learning, Computer Vision
\end{itemize}

\educationEntry{Suffolk University, Boston, MA}{September 2021 -- May 2023}
\begin{itemize}
    \item Bachelor of Science in Computer Science; Cum Laude; GPA: 3.5/4.0
\end{itemize}

\educationEntry{INTI International College Subang, Malaysia}{September 2019 -- July 2021}
\begin{itemize}
    \item Bachelor of Science in Computer Science (Transfer Program)
\end{itemize}

\educationEntry{Tashkent University of Information Technologies, Uzbekistan}{September 2017 -- June 2019}
\begin{itemize}
    \item Bachelor of Science in Software Engineering
\end{itemize}

%----------PUBLICATIONS----------
\section{Publications}
\begin{enumerate}[leftmargin=1.4em, itemsep=2pt, label={[\arabic*]}]
    \item S.\ Ilyosbekov, ``MelanomaNet: Explainable Deep Learning for Multi-Class Skin Lesion Classification,'' \textit{arXiv preprint}, arXiv:2512.09289, 2024. \href{https://arxiv.org/abs/2512.09289}{\color{linkcolor}[Paper]}
\end{enumerate}

%----------AWARDS & HONORS----------
\section{Awards \& Honors}
\begin{itemize}[itemsep=2pt]
    \item \textbf{National Physics Olympiad, 1st Place,} Uzbekistan -- First student from my high school to win at national level
    \item \textbf{University Coding Competition Winner,} Tashkent University of Information Technologies
    \item \textbf{Outstanding Project Award,} Bookshelf Scanner -- Computer Vision Course, Northeastern University
\end{itemize}

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{description}
    \item[Deep Learning \& CV:] PyTorch, TensorFlow/Keras, OpenCV, YOLO, EfficientNet, ResNet, U-Net, GradCAM++, CNNs, Vision Transformers, Image Classification, Object Detection, Depth Estimation, Super-Resolution, Explainable AI
    \item[Machine Learning:] Supervised/Unsupervised Learning, Transfer Learning, XGBoost, K-means Clustering, Model Evaluation, Hyperparameter Tuning, NLP
    \item[Languages:] Python, C\#, C++, TypeScript, JavaScript, Kotlin
    \item[Infrastructure:] Docker, Kubernetes, AWS, Azure, CUDA
    \item[Frameworks \& Tools:] .NET, Blazor, SignalR, Prisma, NestJS, ElysiaJS, Next.js, Angular, FastAPI, RabbitMQ, PostgreSQL
\end{description}

%----------RESEARCH PROJECTS----------
\section{Research Projects}

\projectHeadingPaper{MelanomaNet: Explainable Deep Learning for Multi-Class Skin Lesion Classification}
{https://github.com/suxrobgm/explainable-melanoma}
{https://arxiv.org/abs/2512.09289}
\begin{itemize}
    \item Developed an explainable deep learning system for multi-class skin lesion classification across all 9 ISIC 2019 diagnostic categories using EfficientNet V2 with high-resolution (384$\times$384) input; achieved 85.61\% accuracy and 0.8564 weighted F1 on 25{,}331 dermoscopic images.
    \item Implemented GradCAM++ attention visualization and novel ABCDE criterion analysis with automated feature extraction (asymmetry quantification, border irregularity, color variation via K-means, diameter calculation).
    \item Designed GradCAM-ABCDE alignment metrics to validate model attention correlation with clinical dermatological features, producing comprehensive interpretability reports.
    \item \textbf{Stack:} Python, PyTorch, EfficientNet V2, GradCAM++, OpenCV, Focal Loss, ISIC 2019 Dataset
\end{itemize}

\projectHeading{LightDepth: Lightweight Monocular Depth Estimation}
{https://github.com/suxrobgm/lightdepth}
\begin{itemize}
    \item Designed a lightweight depth estimation model using ResNet18 encoder with U-Net decoder and skip connections, achieving competitive accuracy with 42\% fewer parameters (14.3M vs 24.8M) than Depth Anything V2.
    \item Achieved 72\% faster inference while outperforming on relative error metrics (5.3\% better AbsRel, 31.1\% better SqRel) on NYU Depth V2.
    \item \textbf{Stack:} Python, PyTorch, ResNet18, U-Net Architecture, L1 Loss, NYU Depth V2 Dataset
\end{itemize}

\projectHeading{FSRCNN: Accelerating Super-Resolution Convolutional Neural Network}
{https://github.com/suxrobgm/fsrcnn}
\begin{itemize}
    \item Implemented FSRCNN for single-image super-resolution (Dong et al., ECCV 2016), achieving 40$\times$ speedup over SRCNN with end-to-end learned upsampling at 2$\times$, 3$\times$, and 4$\times$ scales.
    \item Evaluated on Set5 (+1.78\,dB PSNR, +0.0507 SSIM) and Set14 (+1.26\,dB PSNR, +0.0477 SSIM) with ablation studies.
    \item \textbf{Stack:} Python, PyTorch, Mixed Precision Training (AMP), T91/Set5/Set14/DIV2K Datasets
\end{itemize}

\projectHeading{Bookshelf Scanner: Multi-Modal Book Detection and Recognition}
{https://github.com/suxrobgm/bookshelf-scanner}
\begin{itemize}
    \item Built an end-to-end pipeline combining YOLO segmentation for book instance detection with Moondream2 vision-language model for title/author extraction from bookshelf images.
    \item Integrated object segmentation with LLMs for multi-modal understanding and text recognition.
    \item \textbf{Stack:} Python, YOLO, Moondream2 LLM, Llama CPP, PyTorch, FastAPI, Angular
\end{itemize}

\projectHeading{AoE4 Matchmaking: ML-Assisted Player Matching System}
{https://github.com/suxrobgm/aoe4-matchmaking}
\begin{itemize}
    \item Designed ML-assisted matchmaking combining unsupervised player clustering, XGBoost outcome prediction, and ELO rating for balanced competitive matches.
    \item Applied feature engineering on player statistics and ensemble methods to optimize match pairing.
    \item \textbf{Stack:} Python, XGBoost, K-means Clustering, Pandas, NumPy, FastAPI, Angular
\end{itemize}

%----------WORK EXPERIENCE----------
\section{Work Experience}

\experienceEntry{Senior Software Engineer}{EmTech Care Labs}{Portland, ME}{Jan 2025 -- Jun 2025}
\begin{itemize}
    \item Architected and shipped a HIPAA-compliant care-coordination platform on AWS Amplify serving 200+ caregivers and patients, with real-time messaging, push notifications, and shared care-plan editing for collaborative Alzheimer's care.
    \item Led AWS Amplify Gen 1 to Gen 2 migration across the codebase, cutting deploy time from 12 to 7 minutes (40\%) and reducing monthly CI spend by \textasciitilde\$800.
    \item Consolidated 3 fragmented frontends into a single TypeScript monorepo and design system of 40+ shared components, cutting new-screen build time from days to hours and eliminating UI drift between web and mobile.
    \item Hardened the platform for HIPAA: field-level PHI encryption, audit logging via DynamoDB Streams, and Cognito-based RBAC; cleared a third-party HIPAA readiness assessment with zero critical findings.
    \item Owned end-to-end delivery as the sole senior engineer: scoped requirements with clinicians, shipped 10+ features in 6 months, and mentored 2 junior engineers through onboarding and code review.
\end{itemize}

\experienceEntry{Senior Software Engineer}{AllFactors}{Santa Clara, CA}{July 2022 -- Dec 2023}
\begin{itemize}
    \item Drove migration of a legacy ASP.NET Web Forms real-estate analytics application to Blazor WebAssembly, cutting initial page load from 4.2s to 2.1s, shrinking bundle size by 35\%, and removing all ViewState dependencies.
    \item Designed and shipped a Blazor component library of 30+ responsive UI primitives (data grids, charts, filters), reducing new-page implementation time from \textasciitilde3 days to \textasciitilde6 hours and standardizing dashboards across the product.
    \item Built a real-time market-data pipeline using SignalR and SQL Server change tracking, pushing pricing and inventory updates to 500+ concurrent users with sub-200ms end-to-end latency.
    \item Introduced an automated test suite (xUnit + Playwright) covering critical user flows, raising code coverage from 12\% to 68\% and catching 30+ regressions before release.
\end{itemize}

\experienceEntry{Software Engineer}{Smart Meal Service}{Russia}{Sep 2020 -- Oct 2021}
\begin{itemize}
    \item Developed a robotic cashier and self-service kiosk in C\# / .NET processing 500+ daily transactions, integrating with POS terminals and payment hardware over TCP/IP and serial protocols.
    \item Shipped a customer mobile ordering app (Xamarin) and admin dashboard (ASP.NET Core + Angular), cutting average kitchen ticket time by \textasciitilde25\% through automated order routing.
    \item Built a hardware abstraction layer that let the same kiosk software run across 3 machine variants, reducing per-store deployment from \textasciitilde2 days to under 4 hours.
\end{itemize}

\experienceEntry{Game Developer}{Pentalight Technology}{Malaysia}{Mar 2020 -- Feb 2021}
\begin{itemize}
    \item Built multiplayer networking for a VR smart-city simulation in Unity, supporting 20+ concurrent users with sub-100ms state sync via MLAPI and SteamVR.
    \item Implemented spatial audio, hand-tracking, and HUD systems, plus a spectator/desktop client so non-VR participants could observe and interact with the world in real time.
    \item Authored an asset pipeline automating FBX import, LOD generation, and lightmap baking, cutting per-scene iteration from 4 hours to 20 minutes.
\end{itemize}

\vspace{5pt}\noindent
{\color{lighttext}\textit{Earlier:} Game Developer at EC Dev Team, Uzbekistan (2016--19) -- Led RTS game development in Clausewitz Engine. Freelance Developer at Freelancer.com (2019--20) -- .NET and Python NLP applications.}

%----------SELECTED SOFTWARE PROJECTS----------
\section{Selected Software Projects}

\personalProject{LogisticsX}{AI-first multi-tenant fleet management platform with a Claude-API agentic dispatcher (custom MCP server) that autonomously matches loads, verifies HOS/FMCSA compliance, and optimizes routes; 4 Angular 21 portals + Kotlin Multiplatform driver app on a .NET 10 / EF Core / SignalR backend with DAT, Truckstop, Samsara, and Stripe Connect integrations.}{https://logisticsx.app}
\personalProject{Meat.gg}{CS2 community platform serving 30K+ users and 1K+ DAU with social features and a Stripe-backed cosmetic shop, paired with a custom Metamod:Source 2 plugin (C++23) bridging game servers to an ElysiaJS backend over WebSockets for in-game ban/report/admin workflows.}{https://meat.gg}
\personalProject{OGStack}{SaaS that auto-generates on-brand Open Graph images for any URL via a single meta tag; multi-model AI routing (Claude/GPT/DeepSeek), Flux 2 backgrounds, Satori JSX$\rightarrow$SVG$\rightarrow$PNG rendering, Stripe subscriptions, sub-200ms p95 via Cloudflare R2/CDN (10K+ images during beta).}{https://ogstack.dev}
\personalProject{DepVault}{Dependency scanner and encrypted secrets vault covering 8+ language ecosystems (npm, PyPI, NuGet, Cargo, Maven, Go, RubyGems, Composer) with CVE detection via OSV.dev, AES-256-GCM envelope encryption, one-time secret sharing, and a .NET AOT CLI for CI/CD token injection.}{https://depvault.com}
\personalProject{Med Image Scanner}{HIPAA-compliant platform connecting to hospital PACS over DICOM C-FIND/C-MOVE to retrieve X-ray, CT, and MRI studies; runs PyTorch detection models (pneumonia on CXR, intracranial hemorrhage on head CT) with overlays rendered in the OHIF Viewer.}{https://github.com/suxrobgm/med-image-scanner}

\end{document}
