%-------------------------
% Resume - Sukhrob Ilyosbekov
% Senior Full-Stack Developer / Game Developer / CV Researcher
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{multicol}

% Colors
\definecolor{accent}{HTML}{2B5797}
\definecolor{darktext}{HTML}{1A1A1A}
\definecolor{lighttext}{HTML}{444444}
\definecolor{linkcolor}{HTML}{0563C1}
\definecolor{rulecolor}{HTML}{2B5797}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdfborderstyle={/S/U/W 0},
}

% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Section formatting - colored rule
\titleformat{\section}{
    \color{darktext}\large\bfseries\scshape
}{}{0em}{}[{\color{rulecolor}\vspace{2pt}\titlerule\vspace{1pt}}]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Tighter list spacing
\setlist[itemize]{leftmargin=1.4em, itemsep=1pt, parsep=0pt, topsep=2pt}
\setlist[description]{leftmargin=0pt, labelsep=0.5em, font=\bfseries\color{darktext}, style=unboxed, itemsep=1pt}

% --- Education: single row - University, Degree, Location, Date ---
\newcommand{\educationEntry}[4]{%
    \vspace{2pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\color{accent}#1}, {\color{darktext}#2}, {\color{lighttext}#3} & \textit{\color{lighttext}#4} \\
    \end{tabular*}\par\vspace{-1pt}
}

% --- Experience: single-line role | company | location, date right-aligned ---
\newcommand{\experienceEntry}[4]{%
    \vspace{5pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\color{darktext}#1} {\color{lighttext}\textbar} {\color{accent}#2} {\color{lighttext}\textbar} {\color{lighttext}#3} & \textit{\color{lighttext}#4} \\
    \end{tabular*}\vspace{-4pt}
}

% --- Experience: no location variant ---
\newcommand{\experienceEntryNoLoc}[3]{%
    \vspace{5pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\color{darktext}#1} {\color{lighttext}\textbar} {\color{accent}#2} & \textit{\color{lighttext}#3} \\
    \end{tabular*}\vspace{-4pt}
}

% --- Project: name + link on first line, tech stack on second ---
\newcommand{\projectEntry}[3]{%
    \vspace{4pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        {\textbf{\color{accent}#1}} & {\small\href{#3}{\color{linkcolor}#3}} \\
    \end{tabular*}\vspace{-3pt}\\
    {\small\color{lighttext}\textit{#2}}\vspace{-2pt}
}

% --- Project: dual links (site + repo, or repo + paper) ---
\newcommand{\projectEntryDual}[4]{%
    \vspace{4pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        {\textbf{\color{accent}#1}} & {\small\href{#3}{\color{linkcolor}#3} \enspace\color{lighttext}\textbar\enspace \href{#4}{\color{linkcolor}GitHub}} \\
    \end{tabular*}\vspace{-3pt}\\
    {\small\color{lighttext}\textit{#2}}\vspace{-2pt}
}

% --- Project: dual links with Paper label ---
\newcommand{\projectEntryPaper}[4]{%
    \vspace{4pt}\noindent
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        {\textbf{\color{accent}#1}} & {\small\href{#3}{\color{linkcolor}GitHub} \enspace\color{lighttext}\textbar\enspace \href{#4}{\color{linkcolor}Paper}} \\
    \end{tabular*}\vspace{-3pt}\\
    {\small\color{lighttext}\textit{#2}}\vspace{-2pt}
}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\bfseries\color{darktext} Sukhrob Ilyosbekov}\vspace{4pt}\\
    {\large\color{accent} Senior Software Engineer \enspace\textperiodcentered\enspace Full-Stack \& AI}\vspace{8pt}\\
    {\color{lighttext}
    \faPhone\enspace(857) 867-1942 \quad
    \faEnvelope\enspace\href{mailto:silyosbekov@gmail.com}{silyosbekov@gmail.com} \quad
    \faGlobe\enspace\href{https://suxrobgm.net}{suxrobgm.net} \quad
    \faLinkedin\enspace\href{https://www.linkedin.com/in/suxrobgm}{linkedin.com/in/suxrobgm} \quad
    \faGithub\enspace\href{https://github.com/suxrobgm}{github.com/suxrobgm}
    }
\end{center}

%----------PROFESSIONAL SUMMARY----------
\section{Summary}
Senior Software Engineer with 9+ years shipping scalable web apps, SaaS platforms, AI products, and multiplayer games across healthcare, real estate, logistics, and gaming. Deep experience with HIPAA-compliant systems, real-time architectures, and LLM-powered applications; published computer-vision research (arXiv) in explainable AI for medical imaging.

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{description}
    \item[Languages:] C\#, C++, Python, JavaScript, TypeScript, Kotlin
    \item[Backend:] ASP.NET Core, EF Core, SignalR, Node.js, Bun, NestJS, FastAPI, ElysiaJS
    \item[Frontend \& Mobile:] React, Next.js, Angular, Blazor, Tailwind CSS, Kotlin Multiplatform, .NET MAUI, React Native
    \item[Data:] PostgreSQL, MS SQL, MongoDB, Redis, Firebase, DynamoDB, Prisma
    \item[AI/ML:] PyTorch, TensorFlow, OpenCV, YOLO, Claude/GPT/DeepSeek APIs, MCP, agentic workflows
    \item[Game Dev:] Unity, Godot, PhaserJS, Colyseus, Metamod:Source 2
    \item[Cloud \& DevOps:] AWS (Amplify, S3, Lambda, Cognito), Azure, Docker, Kubernetes, GitHub Actions
\end{description}

%----------EDUCATION----------
\section{Education}
\educationEntry{Northeastern University}{M.S.\ in Computer Science}{Boston, MA}{Jan 2024 -- May 2026}
\educationEntry{Suffolk University}{B.S.\ in Computer Science}{Boston, MA}{Sep 2021 -- May 2023}
\educationEntry{INTI International College Subang}{B.S.\ in Computer Science}{Malaysia}{Sep 2019 -- Jul 2021}
\educationEntry{TUIT}{B.S.\ in Software Engineering}{Uzbekistan}{Sep 2017 -- Jun 2019}

%----------PROFESSIONAL EXPERIENCE----------
\section{Professional Experience}

\experienceEntry{Senior Software Engineer}{EmTech Care Labs}{Portland, ME}{Jan 2025 -- Jun 2025}
\begin{itemize}
    \item Architected and shipped a HIPAA-compliant care-coordination platform on AWS Amplify serving 200+ caregivers and patients, with real-time messaging, push notifications, and shared care-plan editing for collaborative Alzheimer's care.
    \item Led AWS Amplify Gen 1 to Gen 2 migration across the codebase, cutting deploy time from 12 to 7 minutes (40\%) and reducing monthly CI spend by \textasciitilde\$800.
    \item Consolidated 3 fragmented frontends into a single TypeScript monorepo and design system of 40+ shared components, cutting new-screen build time from days to hours and eliminating UI drift between web and mobile.
    \item Hardened the platform for HIPAA: field-level PHI encryption, audit logging via DynamoDB Streams, and Cognito-based RBAC; cleared a third-party HIPAA readiness assessment with zero critical findings.
    \item Owned end-to-end delivery as the sole senior engineer: scoped requirements with clinicians, shipped 10+ features in 6 months, and mentored 2 junior engineers through onboarding and code review.
\end{itemize}

\experienceEntry{Senior Software Engineer}{AllFactors}{Santa Clara, CA}{July 2022 -- Dec 2023}
\begin{itemize}
    \item Drove migration of a legacy ASP.NET Web Forms real-estate analytics application to Blazor WebAssembly, cutting initial page load from 4.2s to 2.1s, shrinking bundle size by 35\%, and removing all ViewState dependencies.
    \item Designed and shipped a Blazor component library of 30+ responsive UI primitives (data grids, charts, filters), reducing new-page implementation time from \textasciitilde3 days to \textasciitilde6 hours and standardizing dashboards across the product.
    \item Built a real-time market-data pipeline using SignalR and SQL Server change tracking, pushing pricing and inventory updates to 500+ concurrent users with sub-200ms end-to-end latency.
    \item Introduced an automated test suite (xUnit + Playwright) covering critical user flows, raising code coverage from 12\% to 68\% and catching 30+ regressions before release.
\end{itemize}

\experienceEntry{Software Engineer}{Smart Meal Service}{Russia}{Sep 2020 -- Oct 2021}
\begin{itemize}
    \item Developed a robotic cashier and self-service kiosk in C\# / .NET processing 500+ daily transactions, integrating with POS terminals and payment hardware over TCP/IP and serial protocols.
    \item Shipped a customer mobile ordering app (Xamarin) and admin dashboard (ASP.NET Core + Angular), cutting average kitchen ticket time by \textasciitilde25\% through automated order routing.
    \item Built a hardware abstraction layer that let the same kiosk software run across 3 machine variants, reducing per-store deployment from \textasciitilde2 days to under 4 hours.
\end{itemize}

\experienceEntry{Game Developer}{Pentalight Technology}{Malaysia}{Mar 2020 -- Feb 2021}
\begin{itemize}
    \item Built multiplayer networking for a VR smart-city simulation in Unity, supporting 20+ concurrent users with sub-100ms state sync via MLAPI and SteamVR.
    \item Implemented spatial audio, hand-tracking, and HUD systems, plus a spectator/desktop client so non-VR participants could observe and interact with the world in real time.
    \item Authored an asset pipeline automating FBX import, LOD generation, and lightmap baking, cutting per-scene iteration from 4 hours to 20 minutes.
\end{itemize}

\vspace{5pt}\noindent
{\color{lighttext}\textit{Earlier:} Game Developer at EC Dev Team, Uzbekistan (2016--19) -- Led RTS game development in Clausewitz Engine. Freelance Developer at Freelancer.com (2019--20) -- .NET and Python NLP applications.}

%----------FEATURED PROJECTS----------
\section{Featured Projects}

\projectEntryDual{LogisticsX}{.NET 10, EF Core, MediatR, SignalR, Angular 21, Kotlin KMP, PostgreSQL, Claude API, Stripe, Docker}
{https://logisticsx.app}
{https://github.com/suxrobgm/logistics-app}
\begin{itemize}
    \item Built an agentic dispatcher on the Claude API (custom MCP server, tool-use loop, structured reasoning traces) that autonomously matches loads to trucks, verifies HOS/FMCSA compliance, and optimizes multi-stop routes -- replacing \textasciitilde15-minute manual dispatch decisions with sub-30-second AI ones.
    \item Shipped 4 Angular 21 portals (admin, dispatcher, customer, broker) plus a Kotlin Multiplatform driver app (Android/iOS) on a multi-tenant .NET 10 / EF Core / SignalR backend, with DAT, Truckstop, 123Loadboard load-board integrations, Samsara/Motive ELD, and Stripe Connect payouts.
\end{itemize}

\projectEntry{Meat.gg}{ElysiaJS, Next.js, PostgreSQL, Prisma, Bun, C++23, Metamod:Source 2, Docker, Stripe}
{https://meat.gg}
\begin{itemize}
    \item Launched a community platform for CS2 servers reaching 30K+ registered users and 1K+ daily active players, with profiles, messaging, friend graph, and a Stripe-backed cosmetic shop processing 100+ monthly transactions.
    \item Wrote a Metamod:Source 2 server plugin in C++23 that bridges CS2 game servers with the ElysiaJS backend over WebSockets, enabling in-game ban/report/admin workflows with sub-500ms round-trip without relying on RCON.
\end{itemize}

\projectEntryDual{OGStack}{Next.js 16, Elysia, Bun, PostgreSQL, Prisma, Satori, Cloudflare R2, Stripe, Docker}
{https://ogstack.dev}
{https://github.com/suxrobgm/ogstack}
\begin{itemize}
    \item SaaS that auto-generates on-brand Open Graph images for any URL via a single meta tag, serving cached images under 200ms p95 via Cloudflare R2 + CDN; generated 10K+ images during beta.
    \item Built a multi-model AI routing layer (Claude, GPT, DeepSeek) for page-content analysis and brand extraction, plus Flux 2 background generation and a Satori-based JSX$\rightarrow$SVG$\rightarrow$PNG renderer with Stripe-billed subscriptions.
\end{itemize}

\projectEntryDual{DepVault}{Next.js, ElysiaJS, PostgreSQL, Prisma, Bun, .NET AOT CLI, Docker}
{https://depvault.com}
{https://github.com/suxrobGM/depvault}
\begin{itemize}
    \item Dependency scanner and encrypted secrets vault covering 8+ language ecosystems (npm, PyPI, NuGet, Cargo, Maven, Go, RubyGems, Composer) with CVE detection via OSV.dev, AES-256-GCM envelope encryption, one-time secret sharing, and a .NET AOT CLI for CI/CD token injection.
    \item Designed a streaming SBOM ingestion pipeline (Elysia + Bun) that scans 1K+ dependencies per project in under 5 seconds, with deduplicated vulnerability normalization across OSV, GHSA, and NVD feeds.
\end{itemize}

\projectEntry{Med Image Scanner}{FastAPI, Next.js, PyTorch, OpenCV, OHIF Viewer, PostgreSQL}
{https://github.com/suxrobgm/med-image-scanner}
\begin{itemize}
    \item HIPAA-compliant platform that connects to hospital PACS over DICOM C-FIND/C-MOVE to retrieve X-ray, CT, and MRI studies, running PyTorch detection models (pneumonia on CXR, intracranial hemorrhage on head CT) with overlays rendered in the OHIF Viewer.
    \item Implemented end-to-end PHI handling -- on-the-fly de-identification, audit logging, role-based study access -- and achieved sub-2s round-trip from PACS query to AI overlay on a 512-slice CT.
\end{itemize}

\projectEntry{Bookshelf Scanner}{YOLO, Moondream2 LLM, FastAPI, Angular}
{https://github.com/suxrobgm/bookshelf-scanner}
\begin{itemize}
    \item Built an end-to-end book-detection pipeline: YOLO segmentation isolates individual book spines from shelf photos at \textasciitilde92\% mAP@0.5, then Moondream2 VLM extracts title and author with \textasciitilde85\% string-match accuracy.
    \item Wrapped the pipeline in a FastAPI service with an Angular frontend supporting upload, manual edit, and bulk export to Goodreads/LibraryThing CSV.
\end{itemize}

\projectEntryPaper{MelanomaNet}{PyTorch, EfficientNet V2, GradCAM++, OpenCV}
{https://github.com/suxrobgm/explainable-melanoma}
{https://arxiv.org/abs/2512.09289}
\begin{itemize}
    \item Trained an EfficientNet V2 classifier on the ISIC 2019 dataset (25K+ dermoscopic images, 9 diagnostic categories), achieving 85.61\% accuracy and a 0.8564 weighted F1 score.
    \item Layered GradCAM++ heatmaps with a novel ABCDE-criterion (Asymmetry, Border, Color, Diameter, Evolution) decomposition for clinician-readable interpretability; method published on arXiv (2512.09289).
\end{itemize}

\end{document}
